---
title: How I got into the Hall of Fame
header-includes:
  - \usepackage{xcolor}
  - \usepackage{lipsum}
affiliation:
  ## use one only of the following
  # author-columnar: true         ## one column per author
  #institution-columnar: true  ## one column per institution (multiple autors eventually)
  wide: true                  ## one column wide author/affiliation fields

  institution:
    - name: Universitat Politècnica de Catalunya
      department: Computer Science
      location: C/ Jordi Girona 1, Barcelona
      mark: 1
      author:
        - name: Unai Perez Mendizabal
          email: unai.perez.mendizabal@est.fib.upc.edu
        - name: Damian Rubio Cuervo
          email: damian.rubio.cuervo@est.fib.upc.edu
abstract: |
  The abstract goes here.
  On multiple lines eventually.

#bibliography: mybibfile.bib
output: rticles::ieee_article
---

```{r include=F}
baseball.dataset <- read.csv("../baseball.csv", na.strings = c('?'),
    colClasses = c("character", rep("integer", 11), rep("double", 4), rep("factor", 2)))
```

#Introduction

Some bullshit to make an introduction into the dataset: \lipsum[1]

# Data preprocessing

In the case of class target `Hall_Of_Fame`, which is a factor, both values 1 and 2 count as being in the hall of fame. The different values make a reference to the evaluation committee that accepted the players into the hall. Thus, this variable will be modified so that it only contains two values, `no` when the player has not been included in the hall of fame and `yes` otherwise.

```{r include=FALSE, cache=F}
levels(baseball.dataset$Hall_of_Fame) <- c("no", "BBWAA", "VC")
```

The name `ELMER_SMITH` is duplicated. A quick search in Wikipedia tells us that there are two former players by the name of Elmer Smith. The data matches: One had played 10 seasons and the other 14, so it is not mistaken data, and removing it could cause data loss. According to Wikipedia, the one that played 14 seasons is however more generally known as Mike Smith. So its name will be replaced to `MIKE_SMITH`, which does not match any other player in the set.

```{r include=FALSE, cache=F}
baseball.dataset[baseball.dataset$Player == "ELMER_SMITH" & baseball.dataset$Number_seasons == 14, "Player"] <- "MIKE_SMITH"
```

The names are originally considered as a variable. They are going to be used as the row names and the variable is going to be removed.

```{r include=FALSE, cache=F}
rownames(baseball.dataset) <- baseball.dataset$Player
baseball.dataset$Player <- NULL
```

# Data exploration

Now we have to explore the data and obtain some basic graphs and conclusions: \lipsum[1]

<!-- An example of a floating figure using the graphicx package. -->
<!-- Note that \label must occur AFTER (or within) \caption. -->
<!-- For figures, \caption should occur after the \includegraphics. -->
<!-- Note that IEEEtran v1.7 and later has special internal code that -->
<!-- is designed to preserve the operation of \label within \caption -->
<!-- even when the captionsoff option is in effect. However, because -->
<!-- of issues like this, it may be the safest practice to put all your -->
<!-- \label just after \caption rather than within \caption{}. -->

<!-- Reminder: the "draftcls" or "draftclsnofoot", not "draft", class -->
<!-- option should be used if it is desired that the figures are to be -->
<!-- displayed while in draft mode. -->

<!-- \begin{figure}[!t] -->
<!-- \centering -->
<!-- \includegraphics[width=2.5in]{myfigure} -->
<!-- where an .eps filename suffix will be assumed under latex,  -->
<!-- and a .pdf suffix will be assumed for pdflatex; or what has been declared -->
<!-- via \DeclareGraphicsExtensions. -->
<!-- \caption{Simulation results for the network.} -->
<!-- \label{fig_sim} -->
<!-- \end{figure} -->

<!-- Note that the IEEE typically puts floats only at the top, even when this -->
<!-- results in a large percentage of a column being occupied by floats. -->


<!-- An example of a double column floating figure using two subfigures. -->
<!-- (The subfig.sty package must be loaded for this to work.) -->
<!-- The subfigure \label commands are set within each subfloat command, -->
<!-- and the \label for the overall figure must come after \caption. -->
<!-- \hfil is used as a separator to get equal spacing. -->
<!-- Watch out that the combined width of all the subfigures on a  -->
<!-- line do not exceed the text width or a line break will occur. -->

<!-- \begin{figure*}[!t] -->
<!-- \centering -->
<!-- \subfloat[Case I]{\includegraphics[width=2.5in]{box}% -->
<!-- \label{fig_first_case}} -->
<!-- \hfil -->
<!-- \subfloat[Case II]{\includegraphics[width=2.5in]{box}% -->
<!-- \label{fig_second_case}} -->
<!-- \caption{Simulation results for the network.} -->
<!-- \label{fig_sim} -->
<!-- \end{figure*} -->

<!-- Note that often IEEE papers with subfigures do not employ subfigure -->
<!-- captions (using the optional argument to \subfloat[]), but instead will -->
<!-- reference/describe all of them (a), (b), etc., within the main caption. -->
<!-- Be aware that for subfig.sty to generate the (a), (b), etc., subfigure -->
<!-- labels, the optional argument to \subfloat must be present. If a -->
<!-- subcaption is not desired, just leave its contents blank, -->
<!-- e.g., \subfloat[]. -->


<!-- An example of a floating table. Note that, for IEEE style tables, the -->
<!-- \caption command should come BEFORE the table and, given that table -->
<!-- captions serve much like titles, are usually capitalized except for words -->
<!-- such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to -->
<!-- and up, which are usually not capitalized unless they are the first or -->
<!-- last word of the caption. Table text will default to \footnotesize as -->
<!-- the IEEE normally uses this smaller font for tables. -->
<!-- The \label must come after \caption as always. -->

<!-- \begin{table}[!t] -->
<!-- % increase table row spacing, adjust to taste -->
<!-- \renewcommand{\arraystretch}{1.3} -->
<!-- if using array.sty, it might be a good idea to tweak the value of -->
<!-- \extrarowheight as needed to properly center the text within the cells -->
<!-- \caption{An Example of a Table} -->
<!-- \label{table_example} -->
<!-- \centering -->
<!-- % Some packages, such as MDW tools, offer better commands for making tables -->
<!-- % than the plain LaTeX2e tabular which is used here. -->
<!-- \begin{tabular}{|c||c|} -->
<!-- \hline -->
<!-- One & Two\\ -->
<!-- \hline -->
<!-- Three & Four\\ -->
<!-- \hline -->
<!-- \end{tabular} -->
<!-- \end{table} -->


<!-- Note that the IEEE does not put floats in the very first column -->
<!-- - or typically anywhere on the first page for that matter. Also, -->
<!-- in-text middle ("here") positioning is typically not used, but it -->
<!-- is allowed and encouraged for Computer Society conferences (but -->
<!-- not Computer Society journals). Most IEEE journals/conferences use -->
<!-- top floats exclusively.  -->
<!-- Note that, LaTeX2e, unlike IEEE journals/conferences, places -->
<!-- footnotes above bottom floats. This can be corrected via the -->
<!-- \fnbelowfloat command of the stfloats package. -->


Conclusion
============
The conclusion goes here.

<!-- conference papers do not normally have an appendix -->

Acknowledgment {#acknowledgment}
==============

The authors would like to thank...

Bibliography styles
===================

<!-- Here are two sample references: @Feynman1963118 [@Dirac1953888]. -->

<!--\newpage-->
<!--References {#references .numbered}-->
